\documentclass[11pt]{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[a4paper,top=2cm,bottom=2cm,left=2cm,right=2cm,marginparwidth=1.75cm]{geometry}

\usepackage{fontspec}
\setmainfont{Arial}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Project: Java and Web Development\\Hospital Appointment Management System}
\author{Jose Esteban Vasquez Barboza}
\usepackage[yyyymmdd]{datetime}
\renewcommand{\dateseparator}{--}

\begin{document}
    \maketitle

    \newpage

    \section{Use cases}

    The project will be a web application designed to manage the appointments of a Hospital. The purpose is to manage the registration of Clients and Doctors in to the system, as well as the scheduling of appointments.\\ \\
    The target user group is both private and public hospitals and clinics.\\ \\
    The actors and use cases of the system are: \\ 

\textbf{Client}: the client of the application, who will make the appointments. Its use cases are as follows:
    \begin{itemize}
        \item Register in the system.
        \item Log in to the system.
        \item Update user data.
        \item View available dates/hours for appointments.
        \item Schedule an appointment for an available date/hour.
        \item Modify scheduled appointments.
        \item Cancel scheduled appointments. \end{itemize}

\textbf{Doctor}:  its use cases are as follows:
    \begin{itemize}
        \item View all patients who have had appointments.
        \item View patient appointment history. \end{itemize}
    
\textbf{Admin}: its use cases are as follows:
    \begin{itemize}
        \item Accepts user registration in the system.
        \item Registers new doctors in the system.
        \item Modifies user's/doctor's data.
        \item Deletes users/doctors from the system.
    \end{itemize}

    \section{Technologies}
    The following technologies will be used:
    \begin{itemize}
        \item \textbf{Backend}: Java, Spring Boot.
    \end{itemize}
    \begin{itemize}
        \item \textbf{Frontend}: JavaScript, TypeScript, React, Vite, and Tailwind CSS.
    \end{itemize}
    \begin{itemize}
        \item \textbf{Database}: MariaDB.
    \end{itemize}



\end{document}
